Solar-Electric and Gas Powered, Long-Endurance UAV Sizing via Geometric Programming

### 2017-05-22 docs/thesis/chap_results.tex
change naming for tables; update intro conclusion and result sections; add sp reference

The gas and solar-electric powered aircraft optimization models were solved by minimizing the take-off weight for the requirements listed in Table~\ref{t:mreqs}. 
Key design parameters for both aircraft optimization models are listed in Table~\ref{t:gassolarparams}.
The gas powered aircraft optimization model had 552 unknowns and was solved in 0.144 seconds for a max take-off weight of 84.0 lbs.  
The solar-electric powered optimization model had 375 unknowns and was solved in 0.164 seconds for a max take-off weight of 194.7 lbs.
Highlighted design variables for both architectures are listed in Tables~\ref{t:svals} and~\ref{t:gvals} for various mission requirements.
The rest of this chapter explores how these results may vary for different requirements, input parameter values, and physics modeling assumptions.

@@

 \begin{figure}[H]
 \begin{subfigmatrix}{3}% number of columns
  \subfigure[35th Latitude, $p_{\text{wind}}=0.80$]{\includegraphics[natwidth=542,natheight=414]{bcontourl35a80.pdf}}
  \subfigure[35th Latitude, $p_{\text{wind}}=0.85$]{\includegraphics[natwidth=542,natheight=414]{bcontourl35a85.pdf}}
  \subfigure[35th Latitude, $p_{\text{wind}}=0.90$]{\includegraphics[natwidth=542,natheight=414]{bcontourl35a90.pdf}}
  \subfigure[30th Latitude, $p_{\text{wind}}=0.80$]{\includegraphics[natwidth=542,natheight=414]{bcontourl30a80.pdf}}
  \subfigure[30th Latitude, $p_{\text{wind}}=0.85$]{\includegraphics[natwidth=542,natheight=414]{bcontourl30a85.pdf}}
  \subfigure[30th Latitude, $p_{\text{wind}}=0.90$]{\includegraphics[natwidth=542,natheight=414]{bcontourl30a90.pdf}}
  \subfigure[25th Latitude, $p_{\text{wind}}=0.80$]{\includegraphics[natwidth=542,natheight=414]{bcontourl25a80.pdf}}
  \subfigure[25th Latitude, $p_{\text{wind}}=0.85$]{\includegraphics[natwidth=542,natheight=414]{bcontourl25a85.pdf}}
  \subfigure[25th Latitude, $p_{\text{wind}}=0.90$]{\includegraphics[natwidth=542,natheight=414]{bcontourl25a90.pdf}}
 \end{subfigmatrix}
 \caption{\textbf{Maxtrix of minimum wing span solar-electric aircraft designs. Values of assumed constants are given throughout the text.}}
 \label{f:solarcontours}
\end{figure}

@@

Because this equation is not GP-compatible a signomial program is used to solve the optimization model for both the solar-electric and gas powered models.\cite{sp}
The flexibility factor,

@@

is a measure of how the pitch control authority is degraded by the flexibility of the tail boom. 
Thus, it is expected that the horizontal tail volume coefficient will increase from an increased horizontal tail surface area and tail boom length. 
Tables~\ref{t:tbftable} and~\ref{t:tbfgtable} confirm the increased size of the horizontal tail and tail boom when the tail boom flexibility model is activiated.

>>>>

The gas and solar-electric powered aircraft optimization models were solved by minimizing the take-off weight for the requirements listed in Table~\ref{t:mreqs} and the assumptions and key design parameters described herein. 
The solar-electric powered optimization model had 375 unknowns and was solved in 0.164 seconds for a max take-off weight of 194.7 lbs.
The gas powered aircraft optimization model had 552 unknowns and was solved in 0.144 seconds for a max take-off weight of 72.3 lbs.  
Important design parameters are listed in Table~\ref{t:gassolarparams}.
Key design variables for both architectures are listed in Tables~\ref{t:svals} and~\ref{t:gvals} for various mission requirements. 
The rest of this section explores how these result may vary for different requirements, input parameter values, and physics modeling assumptions.

@@

 \begin{figure}[h!]
 \begin{subfigmatrix}{3}% number of columns
  \subfigure[35th Latitude, $p_{\text{wind}}=0.80$]{\includegraphics[natwidth=542,natheight=414]{bcontourl35a80.pdf}}
  \subfigure[35th Latitude, $p_{\text{wind}}=0.85$]{\includegraphics[natwidth=542,natheight=414]{bcontourl35a85.pdf}}
  \subfigure[35th Latitude, $p_{\text{wind}}=0.90$]{\includegraphics[natwidth=542,natheight=414]{bcontourl35a90.pdf}}
  \subfigure[30th Latitude, $p_{\text{wind}}=0.80$]{\includegraphics[natwidth=542,natheight=414]{bcontourl30a80.pdf}}
  \subfigure[30th Latitude, $p_{\text{wind}}=0.85$]{\includegraphics[natwidth=542,natheight=414]{bcontourl30a85.pdf}}
  \subfigure[30th Latitude, $p_{\text{wind}}=0.90$]{\includegraphics[natwidth=542,natheight=414]{bcontourl30a90.pdf}}
  \subfigure[25th Latitude, $p_{\text{wind}}=0.80$]{\includegraphics[natwidth=542,natheight=414]{bcontourl25a80.pdf}}
  \subfigure[25th Latitude, $p_{\text{wind}}=0.85$]{\includegraphics[natwidth=542,natheight=414]{bcontourl25a85.pdf}}
  \subfigure[25th Latitude, $p_{\text{wind}}=0.90$]{\includegraphics[natwidth=542,natheight=414]{bcontourl25a90.pdf}}
 \end{subfigmatrix}
 \caption{\textbf{Maxtrix of minimum wing span solar-electric aircraft designs. Values of assumed constants are given throughout the text.}}
 \label{f:solarcontours}
\end{figure}

@@

Because this equation is not GP-compatible a signomial program is used to solve the optimization model for both the solar-electric and gas powered models.\cite{sp}\cite{gp}
The flexibility factor,

@@

is a measure of how the pitch control authority is degraded by the flexibility of the tail boom. 
Thus, it is expected that the horizontal tail volume coefficient will increase from an increased horizontal tail surface area and tail boom length. 
Tables~\ref{t:tbftable} and~\ref{t:tbfgtable} confirm the increased size of the horizontal tail and tail boom when the tail boom flexibility model is activiated. 
Because tail boom flexibility is strictly worse for aircraft weight because it requires more horizontal tail surface area or more tail boom length it is surprising to see that for the 30$^{\circ}$ latitude case the horizontal tail weight actually decreases on the solar aircraft.  
Adding the additional constraints to account for the tail boom flexibility allows for the horizontal tail aspect ratio to be optimized, whereas before it was a required input. 
The high aspect ratio of the horizontal tails means low interior foam weight even though the surface area is bigger.

### 2017-05-22 docs/thesis/cover.tex
change naming for tables; update intro conclusion and result sections; add sp reference

\author{Michael Burton}
% If you wish to list your previous degrees on the cover page, use the 
% previous degrees command:
%       \prevdegrees{A.A., Harvard University (1985)}
% You can use the \\ command to list multiple previous degrees
%       \prevdegrees{B.S., University of California (1978) \\
%                    S.M., Massachusetts Institute of Technology (1981)}
\prevdegrees{B.S., Massachusetts Institute of Technology (2016)}
\department{Department of Aeronautics and Astronautics}

@@

% If there is more than one supervisor, use the \supervisor command
% once for each.
\supervisor{Warren Hoburg}{Associate Professor}

@@

This is the acknowledgements section.  You should replace this with your
own acknowledgements.

>>>>

\author{Michael Burton}
% If you wish to list your previous degrees on the cover page, use the 
% previous degrees command:
%       \prevdegrees{A.A., Harvard University (1985)}
% You can use the \\ command to list multiple previous degrees
%       \prevdegrees{B.S., University of California (1978) \\
%                    S.M., Massachusetts Institute of Technology (1981)}
\prevdegrees{B.S., Massachusetts Institute of Technology, 2016}
\department{Department of Aeronautics and Astronautics}

@@

% If there is more than one supervisor, use the \supervisor command
% once for each.
\supervisor{Warren Hoburg}{Associate Professor of Aeronautics and Astronautics}

@@

The success I achieved in completing this thesis was only possible because of the incredible support from family, friends, mentors, and MIT faculty.
I was able to complete this thesis a full year ealier than I expected and I must thank the many people who made that possible.

I first need to thank my family beginning with my beautiful wife, Jasmine.  
Her support and encouragement have been unwavering.  
When I was up late struggling with a problem, she never believed I wouldn't figure it out.  
She has always been enthusiastic and supportive of my successes and given sound advice and encouragment when facing difficult problems or situations. 
I could not have done this without her.

My parents and sibilings were also constant sources of support and encouragement. 
My parents are the wisest people I know and I am immensely grateful for their advice.  
They have always pushed me to be the best me and I would not have ever made it to MIT without them.

I want to greatly thank my advisor, Warren Hoburg (Woody), for his guidance, friendship, and belief in my abilities.  
Woody is a demanding advisor, who pushed me to learn, grow, and develop at a pace and intensity that would not have been possible otherwise. 
While rigorous in his pursuit of high quality work, Woody also gave me the flexibility to explore my own interests and taught me to think critically for myself.
He is truly a brillant professor and I was fortunate that he selected me to join his lab this year.

I would not have made it through the rigors and stress of MIT without my best friend and officemate Martin York. 
I could not have shared an office with a more brillant, passionate and fun person. 
Our common interests, beliefs, and mentality gave me freedom to express my views, opinions, challenges and successes without fear of judgement or offense.

I also need to thank the project managers, professors, and sponsors of the Jungle Hawk Owl, John Hansmen, Navid Yazdani, Mark Drela, Warren Hoburg and Tony Tao. 
The original problem developed by this team of professionals, of which architecture would was best for the Jungle Hawk Owl was the basis for my thesis work.
They all acted as mentors to me, teaching me techincally, guiding me in the industry and giving me opportunites to present my work. 
It was a privilege to work with and for these people to build the Jungle Hawk Owl.

Finally, I want to thank the many fellow students I worked with over the past year and a half building and designing the Jungle Hawk Owl.  
We went through an extremely intense and rapid design and build cycle. 
The late nights, long, arduous layups, and successful test flights have forged a camaraderie between us that I will not forget.
